Making Sequential Programs Deterministic

### 2019-04-05 experiments.tex
remove todo
expt todos

For three of the projects, we could not find the flakiness reported in the
NonDex paper.
\todo{Important: give a sentence description of each one.}
\todo{visualee}
\todo{easy-batch}
\todo{vraptor}.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.95\textwidth}
        \begin{verbatim}
    static public FieldAccess get(Class type) {
        ...
        while (nextClass != Object.class) {
            Field[] declaredFields = nextClass.getDeclaredFields();
            ...
        }
    }
        \end{verbatim}
        \caption{Nondeterministic source code from reflectasm.}
        \label{code-reflectasm}
    \end{subfigure}

@@

\Cref{fig:nondex-source} show samples of nondeterministic code from these
benchmarks.
We annotated the benchmarks based on 
assumptions made downstream of the shown code.

@@

Nondex found 14 flaky tests in Apache Commans Lang due to calls
to \<Class.getDeclaredFields>. 
There are only 5 invocations of \<Class.getDeclaredFields>, so annotating 5 lines of source code
would have been sufficient to identify all that nondeterminism.
Having said that, we admit that there could be
significant programmer effort involved in annotating the whole program. On
the other hand, the NonDex authors
state ``we found that manually inspecting these failures was
rather challenging, and we leave it as future work to automate
debugging test failures.''
\TheDeterminismChecker reports source locations
which makes it easier for the programmer to fix issues, and the annotation
effort serves as valuable documentation and prevents regressions.

@@

\todo{Link to det checker repo?}
\todo{If there is time, we could do a second case study, on a program that
  NonDex did not find nondeterminism in.  Our hope would be to find
  nondeterminism that NonDex did not.  Choose a small project that is
  maintained (it has recent commits), so we can communicate with the authors.}

>>>>

For three of the projects, we could not find the flakiness reported in the
NonDex paper.
\todo{Important: give a sentence description of each one.}
\todo{visualee : Class#getDeclaredMethods}
\todo{easy-batch: Class#getDeclaredFields}
\todo{vraptor : Class#getDeclaredFields}.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.95\textwidth}
        \begin{verbatim}
    static public FieldAccess get(Class type) {
        ...
        while (nextClass != Object.class) {
            Field[] declaredFields = nextClass.getDeclaredFields();
            ...
        }
    }
        \end{verbatim}
        \caption{Nondeterministic source code from reflectasm.\vspace{0.5cm}}
        \label{code-reflectasm}
    \end{subfigure}

@@

\Cref{fig:nondex-source} shows samples of nondeterministic code from these
benchmarks.
We annotated the benchmarks based on 
assumptions made downstream of the shown code.

@@

Nondex found 14 flaky tests in Apache Commons Lang due to calls
to \<Class.getDeclaredFields>. 
There are only 5 invocations of \<Class.getDeclaredFields>, so annotating 5 lines of source code
would have been sufficient to identify all that nondeterminism.
Having said that, we admit that there could be
significant programmer effort involved in annotating the whole program. On
the other hand, the NonDex authors
state ``we found that manually inspecting these failures was
rather challenging, and we leave it as future work to automate
debugging test failures.''
\TheDeterminismChecker reports source locations
which makes it easier for the programmer to fix issues, and the annotation
effort serves as valuable documentation and prevents regressions.

@@

%\todo{Link to det checker repo?}
%\todo{If there is time, we could do a second case study, on a program that
%  NonDex did not find nondeterminism in.  Our hope would be to find
%  nondeterminism that NonDex did not.  Choose a small project that is
%  maintained (it has recent commits), so we can communicate with the authors.}
